Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Use unordered list for questions in evaluation section
Added screenshots
Figure for second approach says it's top down

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{boolean-xor.pdf}
\caption{
Rendering intersecting volumes using the Boolean AND with Boolean XOR approach.
First the pieces behind the intersection, colored red, are rendered.  Next the
intersection, colored green, is rendered.  Then the pieces in front of the
intersection, colored blue, are rendered.  A final pass renders the results to
the screen.
}
\label{boolean-xor}
\end{figure}

@@

@@

How fast can they be rendered?
How easy were they to implement?

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{boolean-xor.pdf}
\caption{
Top down view of rendering intersecting volumes using the Boolean AND with
Boolean XOR approach.  First the pieces behind the intersection, colored red,
are rendered.  Next the intersection, colored green, is rendered.  Then the
pieces in front of the intersection, colored blue, are rendered.  A final pass
renders the results to the screen.
}
\label{boolean-xor}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-and-screenshot-1.png}
\caption{Screenshot of Boolean AND.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{boolean-xor-screenshot-1.png}
\caption{Screenshot of Boolean XOR.}
\end{figure}

@@

\begin{itemize}
  \item How fast can they be rendered?
  \item How easy were they to implement?
\end{itemize}
